Functional pant indicators - wetland, indicator documentation

### 2023-05-29 DRAFT_functional_plant_indicators_seminat.Rmd

```{r, echo = F}
#excel_sheets("P:/41201785_okologisk_tilstand_2022_2023/data/ASO/Semi-naturlig_eng_S123_20#22.xlsx")

ASO.sp <- read_excel("P:/41201785_okologisk_tilstand_2022_2023/data/ASO/Semi-naturlig_eng_S123_2022.xlsx", 
                     sheet = "transektregistreringer_4")
ASO.geo <- read_excel("P:/41201785_okologisk_tilstand_2022_2023/data/ASO/Semi-naturlig_eng_S123_2022.xlsx",
                      sheet = "surveyPoint_0")
#head(ASO.sp)
#head(ASO.geo)

@@

Plant indicators from Tyler et al. (2021)
```{r, echo = F}
## Tyler indicator data
## data from cache
ind.dat <-readRDS(paste0(here::here(),"/data/cache/ind.dat.RDS"))
# ind.dat <- read.table("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/functional plant indicators/Tyler et al_Swedish plant indicators.txt",
#                         sep = '\t', header=T, quote = '')
# head(ind.dat)

@@

Generalized species lists NiN
```{r, echo = F}
# data from cache
Eco_State<-readRDS(paste0(here::here(),"/data/cache/Eco_State.RDS"))
# load("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/functional plant indicators/reference from NiN/Eco_State.RData")
# str(Eco_State)
```

@@

```{r, include = F}
load("P:/41201785_okologisk_tilstand_2022_2023/data/FPI_output large files for markdown/ref_lists_seminat.RData")
```

@@

results.seminat <- list()
ind <- unique(seminat.ref.cov.val$Ind)
# choose columns for site description
colnames(ANO.seminat)
results.seminat[['original']] <- ANO.seminat
# drop geometry
st_geometry(results.seminat[['original']]) <- NULL
results.seminat[['original']]

# add columns for indicators
nvar.site <- ncol(results.seminat[['original']])
for (i in 1:length(ind) ) {results.seminat[['original']][,i+nvar.site] <- NA}
colnames(results.seminat[['original']])[(nvar.site+1):(length(ind)+nvar.site)] <- paste(ind)
for (i in (nvar.site+1):(length(ind)+nvar.site) ) {results.seminat[['original']][,i] <- as.numeric(results.seminat[['original']][,i])}
summary(results.seminat[['original']])
#results.seminat[['original']]$Region <- as.factor(results.seminat[['original']]$Region)
results.seminat[['original']]$GlobalID <- as.factor(results.seminat[['original']]$GlobalID)
results.seminat[['original']]$ano_flate_id <- as.factor(results.seminat[['original']]$ano_flate_id)
results.seminat[['original']]$ano_punkt_id <- as.factor(results.seminat[['original']]$ano_punkt_id)
results.seminat[['original']]$hovedoekosystem_punkt <- as.factor(results.seminat[['original']]$hovedoekosystem_punkt)
#results.seminat[['original']]$Hovedoekosystem_rute  <- as.factor(results.seminat[['original']]$Hovedoekosystem_rute )
results.seminat[['original']]$kartleggingsenhet_1m2 <- as.factor(results.seminat[['original']]$kartleggingsenhet_1m2)
results.seminat[['original']]$hovedtype_rute    <- as.factor(results.seminat[['original']]$hovedtype_rute)

# roll out
results.seminat[['scaled']] <- results.seminat[['non-truncated']] <- results.seminat[['original']]
```

@@

          # Light
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Light')]
          results.seminat[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Light),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Light'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Light1'] <- scal() 
            results.seminat[['non-truncated']][i,'Light1'] <- scal.2() 
            results.seminat[['original']][i,'Light1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Light2'] <- scal() 
            results.seminat[['non-truncated']][i,'Light2'] <- scal.2() 
            results.seminat[['original']][i,'Light2'] <- val
          }

          # Moisture
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Moisture')]
          results.seminat[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Moisture),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Moisture'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Moist1'] <- scal() 
            results.seminat[['non-truncated']][i,'Moist1'] <- scal.2() 
            results.seminat[['original']][i,'Moist1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Moist2'] <- scal() 
            results.seminat[['non-truncated']][i,'Moist2'] <- scal.2() 
            results.seminat[['original']][i,'Moist2'] <- val
          }

          # Soil_reaction_pH
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Soil_reaction_pH')]
          results.seminat[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Soil_reaction_pH),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Soil_reaction_pH'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'pH1'] <- scal() 
            results.seminat[['non-truncated']][i,'pH1'] <- scal.2() 
            results.seminat[['original']][i,'pH1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'pH2'] <- scal() 
            results.seminat[['non-truncated']][i,'pH2'] <- scal.2() 
            results.seminat[['original']][i,'pH2'] <- val
          }

          # Nitrogen
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Nitrogen')]
          results.seminat[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Nitrogen),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Nitrogen'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Nitrogen1'] <- scal() 
            results.seminat[['non-truncated']][i,'Nitrogen1'] <- scal.2() 
            results.seminat[['original']][i,'Nitrogen1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Nitrogen2'] <- scal() 
            results.seminat[['non-truncated']][i,'Nitrogen2'] <- scal.2() 
            results.seminat[['original']][i,'Nitrogen2'] <- val
          }

          # Phosphorus
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Phosphorus')]
          results.seminat[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Phosphorus),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Phosphorus'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Phosphorus1'] <- scal() 
            results.seminat[['non-truncated']][i,'Phosphorus1'] <- scal.2() 
            results.seminat[['original']][i,'Phosphorus1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus2' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Phosphorus2'] <- scal() 
            results.seminat[['non-truncated']][i,'Phosphorus2'] <- scal.2() 
            results.seminat[['original']][i,'Phosphorus2'] <- val
          }

          # Grazing_mowing
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Grazing_mowing')]
          results.seminat[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Grazing_mowing),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Grazing_mowing'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Grazing_mowing1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Grazing_mowing1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Grazing_mowing1' & seminat.ref.cov.val$grunn==as.character(results.seminat[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat dataframe
            results.seminat[['scaled']][i,'Grazing_mowing1'] <- scal() 
            results.seminat[['non-truncated']][i,'Grazing_mowing1'] <- scal.2() 
            results.seminat[['original']][i,'Grazing_mowing1'] <- val

>>>>

```{r, echo = F}
# Add data from cache
ASO.sp<-readRDS(paste0(here::here(),"/data/cache/ASO.sp.RDS"))
ASO.geo<-readRDS(paste0(here::here(),"/data/cache/ASO.geo.RDS"))

#excel_sheets("P:/41201785_okologisk_tilstand_2022_2023/data/ASO/Semi-naturlig_eng_S123_20#22.xlsx")

#ASO.sp <- read_excel("P:/41201785_okologisk_tilstand_2022_2023/data/ASO/Semi-naturlig_eng_S123_2022.xlsx",sheet = "transektregistreringer_4")
#ASO.geo <- read_excel("P:/41201785_okologisk_tilstand_2022_2023/data/ASO/Semi-naturlig_eng_S123_2022.xlsx",sheet = "surveyPoint_0")
#head(ASO.sp)
#head(ASO.geo)

@@

Plant indicators from Tyler et al. (2021)
```{r, echo = F}
## Tyler indicator data
## data from cache
ind.dat <-readRDS(paste0(here::here(),"/data/cache/ind.dat.RDS"))

# ind.dat <- read.table("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/functional plant indicators/Tyler et al_Swedish plant indicators.txt",
#                         sep = '\t', header=T, quote = '')
# head(ind.dat)

@@

Generalized species lists NiN
```{r, echo = F}
# data from cache
Eco_State<-readRDS(paste0(here::here(),"/data/cache/Eco_State.RDS"))

# load("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/functional plant indicators/reference from NiN/Eco_State.RData")
# str(Eco_State)
```

@@

```{r, include = F}
# Data from cache
seminat.ref.cov<-readRDS(paste0(here::here(), "/data/cache/seminat.ref.cov.RDS"))

#load("P:/41201785_okologisk_tilstand_2022_2023/data/FPI_output large files for markdown/ref_lists_seminat.RData")
```

@@

results.seminat.ANO <- list()
ind <- unique(seminat.ref.cov.val$Ind)
# choose columns for site description
colnames(ANO.seminat)
results.seminat.ANO[['original']] <- ANO.seminat
# drop geometry
st_geometry(results.seminat.ANO[['original']]) <- NULL
results.seminat.ANO[['original']]

# add columns for indicators
nvar.site <- ncol(results.seminat.ANO[['original']])
for (i in 1:length(ind) ) {results.seminat.ANO[['original']][,i+nvar.site] <- NA}
colnames(results.seminat.ANO[['original']])[(nvar.site+1):(length(ind)+nvar.site)] <- paste(ind)
for (i in (nvar.site+1):(length(ind)+nvar.site) ) {results.seminat.ANO[['original']][,i] <- as.numeric(results.seminat.ANO[['original']][,i])}
summary(results.seminat.ANO[['original']])
#results.seminat.ANO[['original']]$Region <- as.factor(results.seminat.ANO[['original']]$Region)
results.seminat.ANO[['original']]$GlobalID <- as.factor(results.seminat.ANO[['original']]$GlobalID)
results.seminat.ANO[['original']]$ano_flate_id <- as.factor(results.seminat.ANO[['original']]$ano_flate_id)
results.seminat.ANO[['original']]$ano_punkt_id <- as.factor(results.seminat.ANO[['original']]$ano_punkt_id)
results.seminat.ANO[['original']]$hovedoekosystem_punkt <- as.factor(results.seminat.ANO[['original']]$hovedoekosystem_punkt)
#results.seminat.ANO[['original']]$Hovedoekosystem_rute  <- as.factor(results.seminat.ANO[['original']]$Hovedoekosystem_rute )
results.seminat.ANO[['original']]$kartleggingsenhet_1m2 <- as.factor(results.seminat.ANO[['original']]$kartleggingsenhet_1m2)
results.seminat.ANO[['original']]$hovedtype_rute    <- as.factor(results.seminat.ANO[['original']]$hovedtype_rute)

# roll out
results.seminat.ANO[['scaled']] <- results.seminat.ANO[['non-truncated']] <- results.seminat.ANO[['original']]
```

@@

          # Light
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Light')]
          results.seminat.ANO[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Light),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Light'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Light1'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Light1'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Light1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Light2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Light2'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Light2'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Light2'] <- val
          }

          # Moisture
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Moisture')]
          results.seminat.ANO[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Moisture),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Moisture'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Moist1'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Moist1'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Moist1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Moist2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Moist2'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Moist2'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Moist2'] <- val
          }

          # Soil_reaction_pH
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Soil_reaction_pH')]
          results.seminat.ANO[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Soil_reaction_pH),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Soil_reaction_pH'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'pH1'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'pH1'] <- scal.2() 
            results.seminat.ANO[['original']][i,'pH1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='pH2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'pH2'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'pH2'] <- scal.2() 
            results.seminat.ANO[['original']][i,'pH2'] <- val
          }

          # Nitrogen
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Nitrogen')]
          results.seminat.ANO[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Nitrogen),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Nitrogen'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Nitrogen1'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Nitrogen1'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Nitrogen1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Nitrogen2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Nitrogen2'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Nitrogen2'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Nitrogen2'] <- val
          }

          # Phosphorus
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Phosphorus')]
          results.seminat.ANO[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Phosphorus),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Phosphorus'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Phosphorus1'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Phosphorus1'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Phosphorus1'] <- val

            # upper part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Phosphorus2' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Phosphorus2'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Phosphorus2'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Phosphorus2'] <- val
          }

          # Grazing_mowing
          dat <- ANO.sp.ind[ANO.sp.ind$ParentGlobalID==as.character(ANO.seminat$GlobalID[i]),c('art_dekning','Grazing_mowing')]
          results.seminat.ANO[['original']][i,'richness'] <- nrow(dat)
          dat <- dat[!is.na(dat$Grazing_mowing),]

@@

            val <- sum(dat[,'art_dekning'] * dat[,'Grazing_mowing'],na.rm=T) / sum(dat[,'art_dekning'],na.rm=T)
            # lower part of distribution
            ref <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Grazing_mowing1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Rv']
            lim <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Grazing_mowing1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'Gv']
            maxmin <- seminat.ref.cov.val[seminat.ref.cov.val$Ind=='Grazing_mowing1' & seminat.ref.cov.val$grunn==as.character(results.seminat.ANO[['original']][i,"kartleggingsenhet_1m2"]),'maxmin']
            # coercing x into results.seminat.ANO dataframe
            results.seminat.ANO[['scaled']][i,'Grazing_mowing1'] <- scal() 
            results.seminat.ANO[['non-truncated']][i,'Grazing_mowing1'] <- scal.2() 
            results.seminat.ANO[['original']][i,'Grazing_mowing1'] <- val
